Physcraper: A Python package for continually updated gene trees

### 2020-05-20 phylota-overview.Rmd
phylota citations 81-90

    trees [@mcmahon2015stbase], cites phylota as a databse of gene trees or multrees,

@@

    - the study that present DarwinTree [@meng2015darwintree] as well as the study

@@

    to parallelize BLAST [@yong2010screening], both cite phylota as one among other
    "studies based on data mining large numbers of taxa or loci".

@@

    of plants at the kingdom level".
    sequencing. On the same line

@@

@@

      family) [@gomez2020speciation]

@@

>>>>

    trees [@mcmahon2015stbase], cites phylota as a databse of gene trees or mul-trees,

@@

    - the study that present DarwinTree [@meng2015darwintree], the study

@@

    to parallelize BLAST [@yong2010screening], as well as [@meng2014rapidtree] all
    cite phylota as one among other "studies based on data mining large numbers of taxa or loci".
    sequencing.

@@

    of plants at the kingdom level" [@jones2014trends].

@@

    - A study on morphological evolution of electric fish skull, that uses phylotaR
    to retrieve sequences of the family Apteronotidae, order Gymnotiformes [@evans2019bony],
    cites phylota as the inspiration and fundament of phylotaR.
    - A master thesis on SearchTree, a "software tool that allows users to query
    efficiently on an arbitrary user taxon list and returns high scoring matches
    from approximately one billion phylogenetic trees being constructed from molecular
    sequence data in GenBank" [@deepak2010searchtree], that seems to be the preliminary
    work for STBase [@mcmahon2015stbase], cites phylota as "a standard strategy, to assemble sets of homologous sequences
    (clusters) from a database of all-against-all BLAST searches, [in which] clusters
    are constructed in the context of the NCBI taxonomy tree for convenience of display,
    thus child clusters are contained within parent clusters, following the NCBI hierarchy".
    In opposition, SearchTree uses true agglomerative hierarchical clustering
    (AHC: @day1984efficient) based on the BLAST estimates of sequence dissimilarity
    rather than the NCBI tree".
    - a recent review on the state of large phylogeny (namely insects) generation
    using tools of the data-driven era [@chesters2019phylogeny] cites phylota as
    a tool for homology inference and retrieval.
    - the study presenting phylotol [@ceron2019phylotol], cites phylota as a tool
    that "focus on the identification and collection of homologous genes from public
    databases".

@@

    family) [@gomez2020speciation; @gomez2015behavioral]
    - Retrive 145 sequences registered as *Holothuria* species, but kept 84 as ingroup,
    plus 4 outgroup sequences from *Stichopus ocellatus*, all belonging to the order
    Apodida of sea cucumbers [@kamarudin2016phylogenetic]
    - On a master thesis, to get the sequences of the outgroups of Melinidinae, family Poaceae, namely several spp of the
    subfamily Panicoideae, plus *Gynerium sagittatum*, *Chasmanthium latifolium*,
    and *Zea mays*, [@salariato2010filogenia]. Interestingly, phylota was not used
    in the published study of the thesis [@salariato2010molecular]. Ingroup sequences were generated *de novo*.
    - On a PhD thesis, to construct a phylogeny of Platyrrhini (internal group),
    Catarrhini (outgroup), and Tarsiiformes @pereira2013padroes. Have not found a published study.

@@

    - A review by @sanderson2016perspective, takes 134 595 gene trees from phylota
    GenBank rel. 176 and estimates its degree of resolutin, calculating that less
    than half of clades are supported with minilam statistical support (0.53 ± 0.32).

### 2020-05-20 physcraper_ms.Rmd
phylota citations 81-90

@@

SUPERSMART [@antonelli2017toward] - baited analyses up to bayesian divergente time
estimation

@@

>>>>

in @ceron2019phylotol: "pipelines such as AMPHORA (Wu and Eisen 2008) and Mega-phylogeny (Smith et al. 2009) focus on the construction and refinement of robust alignments rather than the collection of homologs"

@@

@papadopoulou2015automated - Automated DNA-based plant identification for large-scale biodiversity assessment

SUPERSMART [@antonelli2017toward] - baited analyses up to bayesian divergence time
estimation

@@

Phylotol [@ceron2019phylotol] - "phylogenomic pipeline to allow easy incorporation
of data from  high-throughput sequencing studies, to automate production of both
multiple sequence alignments and gene trees, and to identify and remove contaminants.
PhyloToL is designed for phylogenomic analyses of diverse lineages across the tree
of life", i.e., bacteria and unicellular eukaryotes.
